---
title: "Project 2"
author: "Shane Hylton"
date: "10/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(stringr)
```

## Loading the Data -- NYC Street Trees

I will load the data and isolate the variables of interest.
Due to the size of the file, I am unable to load the dataframe into github. 

```{r}
treesraw <- read.csv( '/Users/shanehylton/Desktop/fulltrees.csv')
trees <- treesraw[c(10,38,39)]
```

## Plotting a Map of the Data

This suggestion recommended creating a plot of longitude and latitude for each tree. The challenging part of the recommendation will be coloring by species. The plot showed a very interesting outline of New York City. 

```{r}

ggplot(trees, aes(x = longitude, y = latitude, color = spc_common))+
  geom_point()+
  theme(legend.position = "none")+
  scale_x_discrete(labels = NULL, breaks = NULL)+
  ggtitle('Plot of NYC Street Trees')+
  ylab("Latitude")+
  xlab("Longitude")+
  theme(plot.title = element_text(hjust = 0.5))
```

## Analyzing the Lakers' Stats Per Game

Because the only recommendations in the discussion post were to analyze the data, I will refine the dataframe and perform some manipulation. 
I chose to only pay attention to the players I deemed relevant from a points per game point of view. I filtered the dataframe to omit any players who scored fewer than 7 points per game. After this, I noticed that the points per game statistic was at the end of the data frame, so I relocated it to be after the player's name for easy viewing. 

```{r}

link <- url('https://raw.githubusercontent.com/tylerbaker01/DATA-607-Project-2/main/Laker\'s%20Per%20Game%20Stats')
lakersraw <- read.csv(link)
agepts <- lakersraw[c(3, 28)]
relevantlakers <- filter(lakersraw, PTS.G > 7)
relsort <- relevantlakers[order(-relevantlakers$PTS.G), ]
relsort %>%
  relocate(PTS.G, .after = X)


```

## Thread: World Government Indicators
For this step in the project, I took a look at the data Thomas linked and saw that it linked to a number of very wide, untidy Excel sheets. I downloaded one of the sheets and converted it to a .csv. Then I uploaded it to github and loaded it into R for tidying. 
After removing the unnecessary rows, I decided to aggregate the data to represent the mean data for each category over time. I am only interested in countries that existed through the entire data collection period, so I removed all NA entries. 

My final dataframe is sorted by the percentile rank for government effectiveness. 


```{r}

link <- 'https://raw.githubusercontent.com/st3vejobs/Project-2-files/main/government_eff.csv'
govraw <- read.csv(url(link))
gov <- govraw[-c(1:14), ]

names <- c(unlist(c(gov[1, ])))
colnames(gov) <- names
gov <- gov[-c(1), ]
gov[gov=="#N/A"]<-NA
gov <- na.omit(gov)

cols <- c(which(names(gov) == 'Estimate'))
Estimate <- gov[cols]
Estimate[ , c(1:length(Estimate))] <- apply(Estimate[ , c(1:length(Estimate)),drop=F], 2,           
                 function(x) as.numeric(as.character(x)))
Estimate <- rowMeans(Estimate)
finaldf <- data.frame(gov[ , c(1:2)])
finaldf <- cbind(finaldf, Estimate)


cols <- c(which(names(gov) == 'StdErr'))
StdErr <- gov[cols]
StdErr[ , c(1:length(StdErr))] <- apply(StdErr[ , c(1:length(StdErr)),drop=F], 2,           
                 function(x) as.numeric(as.character(x)))
StdErr <- rowMeans(StdErr)
finaldf <- cbind(finaldf, StdErr)

cols <- c(which(names(gov) == 'NumSrc'))
NumSrc <- gov[cols]
NumSrc[ , c(1:length(NumSrc))] <- apply(NumSrc[ , c(1:length(NumSrc)),drop=F], 2,           
                 function(x) as.numeric(as.character(x)))
NumSrc <- rowMeans(NumSrc)
finaldf <- cbind(finaldf, NumSrc)

cols <- c(which(names(gov) == 'Rank'))
Rank <- gov[cols]
Rank[ , c(1:length(Rank))] <- apply(Rank[ , c(1:length(Rank)),drop=F], 2,           
                 function(x) as.numeric(as.character(x)))
Rank <- rowMeans(Rank)
finaldf <- cbind(finaldf, Rank)

cols <- c(which(names(gov) == 'Upper'))
Upper <- gov[cols]
Upper[ , c(1:length(Upper))] <- apply(Upper[ , c(1:length(Upper)),drop=F], 2,           
                 function(x) as.numeric(as.character(x)))
Upper <- rowMeans(Upper)
finaldf <- cbind(finaldf, Upper)

cols <- c(which(names(gov) == 'Lower'))
Lower <- gov[cols]
Lower[ , c(1:length(Lower))] <- apply(Lower[ , c(1:length(Lower)),drop=F], 2,           
                 function(x) as.numeric(as.character(x)))
Lower <- rowMeans(Lower)
finaldf <- cbind(finaldf, Lower)

finalsort <- finaldf[order(-finaldf$Rank), ]
head(finalsort)
```

























